Proportional multi-state multiple-cohort life table model

### 2018-04-24 MSLT/MSLTdoc.Rmd
Loop to age and sex results plot

```{r, echo=TRUE}
plot_eg <- plot_output(in_data = output_df, in_age = 22, in_population = "male", in_outcomes = c("age", "mx_num_bl_ihd", "mx_num_sc_ihd", "mx_num_diff_ihd"), in_legend = "Ischemic Heart Disease Deaths")
```

>>>>

```{r, echo=TRUE}
## Do a loop, the first in_outcomes is age.

i_outcome <- c("mx", "inc")

for (age in i_age_cohort){
  for (sex in i_sex) {
    for (disease in i_disease){
      for (outcome in i_outcome) {
        {
      if (sex == "male" && disease == "breast_cancer"){
        # cat("\n")
      }else{

plot_eg <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_legend = paste(outcome, disease, age, sex, sep = "_"))
          }
        }
      }
    }
  }
}
```
